---
title             : "Reproduing analysis of: Unlearning implicit social biases during sleep (2015)"
shorttitle        : "Unlearning implicit social biases during sleep"

author: 
  - name          : "Richard Troise"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"


affiliation:
  - id            : "1"
    institution   : "Brooklyn College"


authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  There is evidence by @Hu1013 on the unlearning of social bias by reinforcing a counterbias behavior during slow-wave/REM sleep - the optimal time frame to consolidate new memories. The reproduced analysis pertains to the interaction of cued and uncued reduction bias before sleep (prenap), then, one week later (delayed). A power analysis shows that the original effect size may only be observed approximately 14% of the time on average.
  
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "unlearning, social biases, slow-wave sleep"
wordcount         : "X"

bibliography      : ["r-references.bib", "mybib.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
  
  The experiment on unlearning social bias shows the relevance of sleep playing a role in the dissaption of a pre-existing implicit bias, @Hu1013. The rationale comes from auditory information reinforcing learning behavior during slow wave sleep, causing a targeted memory reactivation. As a result of the auditory cue, counterbias behavior in participants was expected to increase. In addition, the memory reactivation should result in a sustained reduction in social bias, in that the measured bias does not differ between prenap and delay. The implications of such an effect may be relevant for unlearning other unwanted habits. The original data was downloaded from [https://osf.io/b3k9a/](https://osf.io/b7x8q/)

# Methods

## Participants
As stated in experiment, there were 40 participants recruited but only 38 were present for all groups.

## Material
The details of the experiment can be found in @Hu1013.

## Procedure
In the reproduced analysis, the 38 participants' bias score were measured under four conditions: No auditory cue before sleep, then one week later; and a reinforced cue before sleep, then one week later.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#downloads csv data into R.
aaa3841_OpenData_withNA <- read.csv("~/GitHub(assignments)/midterm/midterm/aaa3841_OpenData_withNA.csv")

#selecting data for analysis
cue_prenap = aaa3841_OpenData_withNA$Cued_Prenap
cue_delay = aaa3841_OpenData_withNA$Cued_Delayed
uncue_prenap = aaa3841_OpenData_withNA$Uncued_Prenap
uncue_delay = aaa3841_OpenData_withNA$Uncued_Delayed

#preparing new data table of the two factors with IAT scores for each subject
cue_factor = rep(c("C","U"), each = 80)
time_factor = rep(rep(c("D","P"), each = 40), 2)
subjects = aaa3841_OpenData_withNA$Ppt.
sub = as.factor(subjects)
subject_dv = c()


subject_dv =  c(cue_delay[1:length(cue_delay)], cue_prenap[1:length(cue_prenap)], 
                uncue_delay[1:length(uncue_delay)], uncue_prenap[1:length(uncue_prenap)])

# 2-way between subjects anova 
all_data = data.frame(sub, subject_dv, cue_factor, time_factor)
library(dplyr)
nas <- all_data %>%
  filter(is.na(subject_dv)==TRUE)
nas$sub<-as.factor(as.numeric(nas$sub))
bad_subjects <- levels(nas$sub)

clean_df <- all_data %>%
              filter(sub %in% bad_subjects == FALSE)

aov_out = aov(subject_dv~cue_factor*time_factor+Error(sub/(cue_factor*time_factor)), clean_df)
library(papaja)
apa_stuff <- apa_print(summary(aov_out))
#library(sjstats)
#eta_sq(aov_out, partial = TRUE)
```

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses. Two participants had to be excluded from the analyses and were labelled as 'NA' in the data sheet.

# Results
IAT bias scores were grouped in R-studio for each participant in order to perform a 2x2 (cue/uncue vs prenap/delay) repeated measure ANOVA. The group means are displayed in Figure 1 followed by the ANOVA results in Figure 2. There was a main effect of Time, `r apa_stuff$full_result$time_factor`. Mean IAT scores remained lower after training, between prenap testing (0.447) and testing one week later (0.334). There was not a main effect of cue factor after learning, `r apa_stuff$full_result$cue_factor`. The two-way interaction between Time and Cue after training was significant, `r apa_stuff$full_result$cue_factor_time_factor`. The difference in prenap and delay scores was significant only when the cue was not initiated, indicating that memory reactivation sustained after counterbias training.


Figure 1: Means of time and cue factor
```{r, fig1, echo=FALSE, warning=FALSE, message=FALSE}
  library(xtable)
  means = c(mean(cue_prenap), mean(cue_delay, na.rm = TRUE), 
            mean(uncue_prenap), mean(uncue_delay, na.rm = TRUE))
  SEM = c(sd(cue_prenap)/38, sd(cue_delay, na.rm=TRUE)/38, 
          sd(uncue_prenap)/38, sd(uncue_delay, na.rm=TRUE)/38)
  group_means = data.frame(GroupMean=means, Cue=c("Cue","Cue","Uncue","Uncue"), 
                         Time=c("Prenap","Delay","Prenap","Delay"), SEM)
  knitr::kable(xtable(group_means))
```


Figure 2: Results of 2x2 repeated measured ANOVA
```{r, fig2, echo=FALSE, warning=FALSE, message=FALSE}
  knitr::kable(xtable(summary(aov_out)))
```

# Discussion
The interaction result by @Hu1013 was successfully replicated.

## Power Analysis
The replicated interaction was due to a significant difference of the time factor in the uncued group. Since an F-value is equal to the square of a t-value, we can simulate power by simulating a t-test on the difference of time factor. The mean score difference between prenap and delay is (0.143) for cue and uncue. We applied this difference to our simulation assuming equal variance in our two samples (n = 38), and calculated an estimated power of 0.136, meaning the observed effect size may only occur 13.6% of the time.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# function to run a simulated t-test
x = 0.143
sim_power <- function(x){
  A <- rnorm(n=38,mean=0, sd=1)
  B <- rnorm(n=38,mean=(0+x), sd=1)
  return(t.test(A,B,var.equal=TRUE, paired = TRUE)$p.value)
}

# vector of effect sizes
effect_sizes <- seq(.1,2,.1)
# run simulation for each effect size 1000 times
power <- sapply(effect_sizes, 
                FUN = function(x) {
                  sims <- replicate(1000,sim_power(x))
                  sim_power <- length(sims[sims<.05])/length(sims)
                  return(sim_power)})
# combine into dataframe
plot_df <- data.frame(effect_sizes,power)

```

Figure 3.Power analysis on the interaction of time/cue via t-test on time factor
```{r, echo=FALSE, warning=FALSE, message=FALSE}
# plot the power curve
library(ggplot2)
ggplot(plot_df, aes(x=effect_sizes,
                    y=power))+
  geom_point()+
  geom_line()
```


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
