---
title             : "Reproduction of:Unlearning implicit social biases during sleep (2015)"
shorttitle        : "Title"

author: 
  - name          : "Richard Troise"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"


affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"


authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords, more, another"
wordcount         : "X"

bibliography      : ["r-references.bib", "mybib.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

sample citation @Hu1013

second citation @Keith1989



## header

great essay

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

From figure 1.
```{r fig1, fig.cap="figure shows a histogram", fig.width=2, fig.height=3}
a <- rnorm(100,0,1)
hist(a)
```

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
